---
title: "Logistical regression"
format: html
editor: visual
---


#Upload all the packages

```{r}
install.packages("readxl")
library(readxl)
library(tidyverse)
library(dplyr)
```

```{r}
library(readr)
profiles_revised <- read.csv("/Users/radiahkhan/Documents/OkCupid Dataset Analysis/profiles_revised 2.csv")
View(profiles_revised_2)
```

# Preparing the dataset for the prediction models
```{r}
reprod_data <- profiles_revised |>
  rename(Parental_Status = offspring) |>
  mutate(Parental_Status = recode(Parental_Status,
                                  "has a kid" = "Currently a parent",
                                  "doesn&rsquo;t have kids" = "Currently not a parent",
                                  "doesn&rsquo;t want kids" = "Not considering to be a parent",
                                  "wants kids" = "Wants to be a parent",
                                  "has kids, but doesn&rsquo;t want more" = "Currently a parent but not considering multiple",
                                  "has a kid, and wants more" = "Currently a parent and considering multiple",
                                  "might want kids" = "Might consider kids",
                                  "doesn&rsquo;t have kids, and doesn&rsquo;t want any" = "Neither a current parent nor considering to be in future")) |>
  filter(Parental_Status %in% c(
    "Not considering to be a parent", "Currently not a parent", "Wants to be a parent",
    "Currently a parent", "Neither a current parent nor considering to be in future",
    "Currently a parent but not considering multiple",
    "Currently a parent and considering multiple", "Might consider kids")) |>
  mutate(
    sex = recode(sex, "m" = 1, "f" = 0),
    orientation = recode(orientation, "straight" = 1, "gay" = 0, "bisexual" = 0),
    Do_they_want_or_have_or_will_consider_kids = case_when(
      Parental_Status %in% c("Currently a parent", "Wants to be a parent", 
                             "Currently a parent and considering multiple", "Might consider kids") ~ 1,
      TRUE ~ 0)
  ) |>
  select(sex, orientation, Do_they_want_or_have_or_will_consider_kids)

reprod_data
```
```{r}
write.csv(reprod_data, "reprod_data.csv", row.names = FALSE)

```

# Can sex and sexual orientation predict reproduction choices? 

# Do men and women differ in wanting kids? 
Outcome variable here is decision to have kids
Predictor variable here is sex 

```{r}
#Logistical regression Summary (Sex and Reproduction Choices)
fit_sex_reprod <- glm(Do_they_want_or_have_or_will_consider_kids ~ sex,
                family = binomial(link = logit),
                data = reprod_data)

```
```{r}
probabilities_sex_reprod <- predict(fit_sex_reprod, type = "response")
roc_sex <- roc(reprod_data$Do_they_want_or_have_or_will_consider_kids, probabilities_sex_reprod)
auc_sex <- auc(roc_sex)
```
```{r}
pred_vals <- data.frame(sex = c(0, 1))
pred_probs <- predict(fit_sex_reprod, newdata = pred_vals, type = "response")
```
```{r}
barplot(pred_probs, 
        names.arg = c("Female", "Male"),
        main = "Predicted Probability of Wanting/Having Kids by Sex",
        ylab = "Probability",
        xlab = "Sex",
        col = c("darkblue", "lightblue"),
        ylim = c(0, 1))

text(x = 1, y = 0.5, 
     labels = paste("AUC =", round(auc_sex, 4)),
     cex = 1.3, font = 2)
```

The AUC is 0.5478 which is slightly over baseline. Weak predictive power. 


```{r}
fit_orientation_reprod <- glm(Do_they_want_or_have_or_will_consider_kids ~ orientation,
                family = binomial(link = logit),
                data = reprod_data)
summary(fit_orientation_reprod)
```
```{r}
pprobabilities_orientation_reprod <- predict(fit_orientation_reprod, type = "response")
roc_orientation <- roc(reprod_data$Do_they_want_or_have_or_will_consider_kids, probabilities_orientation_reprod)
auc_orientation <- auc(roc_orientation)
```
```{r}
pred_vals_o <- data.frame(orientation = c(0, 1))
pred_probs_o <- predict(fit_orientation_reprod, newdata = pred_vals_o, type = "response") 
```
```{r}
barplot(pred_probs_o, 
        names.arg = c("Queer", "Heterosexual"),  # Changed order and labels
        main = "Predicted Probability of Wanting/Having Kids by Orientation",  # Changed title
        ylab = "Probability",
        xlab = "Orientation",  
        col = c("purple", "blue"), 
        ylim = c(0, 1))

text(x = 1.5, y = 0.9,  
     labels = paste("AUC =", round(auc_orientation, 4)),
     cex = 1.3, font = 2)
```

Results : Both sex and orientation is a weak predictor in determining if someone wants kids. Might be due to effect size. 